--- 
title_meta  : 第二章
title       : 向量
description : "在第二章的課程中，我們要去拉斯維加斯一趟，學習如何在R使用向量分析博弈的結果！當你完成了本章節，你將學會如何宣告向量、命名向量、從向量選取元素以及比較不同的向量。"

--- type:NormalExercise xp:100 skills:1 key:44ae1c0203a5a327a8b7670514bc5c5d07f05a5c
## 宣告向量

覺得自己運氣好嗎？你最好有點自信，本章節帶你到罪惡都市，傳說中的*統計學家天堂*！

你將利用R與資料分析的技巧來提高賭桌上的表現，展開你專業賭徒的職涯。本章節會告訴你如何輕鬆地記錄下注過程以及如何針對這些記錄做簡單的分析，下一站，拉斯維加斯我們來囉！

*** =instructions
- 還記得在第一章學的嗎？宣告一個變數 `vegas` 並且將字串 `"Go!"` 指派給它，要注意大小寫在R是有差別的喔！

*** =hint
在編輯區鍵入以下的程式：
```
vegas <- "Go!"
```

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# 宣告變數vegas
vegas <- 
```

*** =solution
```{r}
# 宣告變數vegas
vegas <- "Go!"
```

*** =sct
```{r}
test_object("vegas", incorrect_msg = "\u78ba\u8a8d\u4f60\u662f\u5426\u6709\u6307\u6d3e\u6b63\u78ba\u7684\u503c\u7d66\u8b8a\u6578 `vegas` \uff0c\u8981\u6ce8\u610f\u5927\u5c0f\u5beb\u5728R\u662f\u6709\u5dee\u5225\u7684\u5594\uff01")
success_msg("\u592a\u68d2\u4e86\uff01\u524d\u9032\u4e0b\u4e00\u500b\u7df4\u7fd2\uff01")
```


--- type:NormalExercise xp:100 skills:1 key:bbc502a52a960a4d3d17fc01945551cb822cdffa
## 宣告向量 (2)

保持專注！ 

在你成為富翁的路上會需要使用到非常多的向量，向量是單一維度的陣列，可以包含數值、文字或者邏輯值。換句話說，向量是一種可以儲存資料的方法，例如將你在賭場中每天贏得的錢與每天損失的錢儲存在向量中。

R使用[`c()`](http://www.rdocumentation.org/packages/base/functions/c)來創造向量，並使用逗號分隔向量中的元素，像是：

```
numeric_vector <- c(1, 2, 3)
character_vector <- c("a", "b", "c")
```

一旦你成功宣告了這些向量，就可以開始進行向量的計算。

*** =instructions 
宣告一個向量 `boolean_vector` 並讓它包含3個元素：`TRUE` 、 `FALSE` 與 `TRUE` (依序). 

*** =hint 
利用 `<-` 指派 `c(TRUE, FALSE, TRUE)` 給變數 `boolean_vector`。

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
numeric_vector <- c(1, 10, 49)
character_vector <- c("a", "b", "c")

# 宣告boolean_vector
boolean_vector <-
```

*** =solution
```{r}
numeric_vector <- c(1, 10, 49)
character_vector <- c("a", "b", "c")

# 宣告boolean_vector
boolean_vector <- c(TRUE, FALSE, TRUE)
```

*** =sct
```{r}
msg <- "\u4e0d\u9700\u8981\u66f4\u6539\u5ba3\u544a `numeric_vector` \u8207 `character_vector` \u7684\u7a0b\u5f0f\u3002"
test_object("numeric_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("character_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("boolean_vector",
            incorrect_msg = "\u78ba\u8a8d\u4f60\u6307\u6d3e\u4e86\u6b63\u78ba\u7684\u503c\u7d66 `boolean_vector`\uff0c\u6b63\u78ba\u7684\u503c\u70ba `c(TRUE, FALSE, TRUE)`\uff0c\u8a18\u5f97\u4e0d\u8981\u5e6b `TRUE` \u6216 `FALSE` \u52a0\u4e0a\u5f15\u865f\uff0c\u540c\u6642\u78ba\u8a8d\u9806\u5e8f\u8207\u8aaa\u660e\u4e00\u6a23\u3002")
success_msg("\u5b8c\u7f8e\uff01\u6ce8\u610f\u6211\u5011\u5728 `c()` \u4e2d\u7684\u9017\u865f\u5f8c\u9762\u52a0\u4e0a\u7a7a\u767d\u662f\u70ba\u4e86\u589e\u52a0\u7a0b\u5f0f\u7684\u53ef\u8b80\u6027\uff0c\u6211\u5011\u6703\u5728\u4e0b\u500b\u7df4\u7fd2\u4e2d\u7df4\u7fd2\u66f4\u591a\u5411\u91cf\u7684\u5ba3\u544a\u3002")
```


--- type:NormalExercise xp:100 skills:1 key:25b255d971d82b1adb868a9bd8a1b583b6c071de
## 宣告向量 (3)

經過一週在賭桌上的奮戰，你還沒有為自己贏到一台法拉利跑車，於是你打算運用資料分析超能力來分析一下過去這週輸贏記錄：

針對樸克牌 `poker_vector`: 

- 星期一贏 \$140
- 星期二輸 \$50
- 星期三贏 \$20 
- 星期四輸 \$120
- 星期五贏 \$240

針對俄羅斯輪盤 `roulette_vector`: 

- 星期一輸 \$24
- 星期二輸 \$50
- 星期三贏 \$100
- 星期四輸 \$350
- 星期五贏 \$10

過去一週你只玩了樸克牌與俄羅斯輪盤，你決定宣告兩個向量 `poker_vector` 與 `roulette_vector`。

*** =instructions
將俄羅斯輪盤的輸贏金額指派給變數 `roulette_vector`。

*** =hint
編輯區已經有了 `poker_vector` 的宣告範例，依樣畫葫蘆你可以順利宣告 `roulette_vector` 並注意輸錢是以負值記錄。

*** =sample_code
```{r}
# 星期一至五的樸克牌贏錢金額
poker_vector <- c(140, -50, 20, -120, 240)

# 星期一至五的俄羅斯輪盤贏錢金額
roulette_vector <-  
```

*** =solution
```{r}
# 星期一至五的樸克牌贏錢金額
poker_vector <- c(140, -50, 20, -120, 240)

# 星期一至五的俄羅斯輪盤贏錢金額
roulette_vector <- c(-24, -50, 100, -350, 10)
```

*** =sct
```{r}
test_object("poker_vector",
            incorrect_msg = "\u78ba\u8a8d\u662f\u5426\u6307\u6d3e\u6b63\u78ba\u7684\u503c\u7d66 `poker_vector`\u3002")
test_object("roulette_vector",
            incorrect_msg = "\u78ba\u8a8d\u662f\u5426\u6307\u6d3e\u6b63\u78ba\u7684\u503c\u7d66 `roulette_vector` \u4e26\u6ce8\u610f\u661f\u671f\u4e00\u81f3\u4e94\u7684\u9806\u5e8f\uff01")
success_msg("\u592a\u597d\u4e86\uff01\u8a18\u5f97\u4f60\u96a8\u6642\u53ef\u4ee5\u5728R Console\u8f38\u5165\u8b8a\u6578\u540d\u7a31\u5f8c\u6309\u8f38\u5165\u9375(Enter)\u6aa2\u67e5\u4f60\u5ba3\u544a\u7684\u5411\u91cf\uff0c\u8b93\u6211\u5011\u524d\u9032\u4e0b\u4e00\u500b\u7df4\u7fd2\uff01")
```


--- type:NormalExercise xp:100 skills:1 key:bfaa5f15a513859fff24771c6d0cd87082211092
## 為向量命名

資料分析師需要對資料有清楚的認知並了解細節，在前一個練習中我們宣告了過去一週的贏錢記錄，如果能夠在向量中顯示出哪個元素屬於哪一天，將會讓你對資料一目瞭然。

你可以使用 `names()` 函數來辦到這件事：

```
some_vector <- c("John Doe", "poker player")
names(some_vector) <- c("Name", "Profession")
```

這段程式首先宣告一個向量 `some_vector` 接著為裡面這兩個元素命名，第一個元素被命名為姓名 `Name` ，第二個元素被命名為職業 `Profession`。在R Console中印出 `some_vector`：

```
          Name     Profession 
    "John Doe" "poker player" 
```

*** =instructions
- 編輯區已經完成 `poker_vector` 的贏錢記錄命名，接者請你對 `roulette_vector` 做一樣的事情。

*** =hint
使用 `names(roulette_vector)` 為 `roulette_vector` 命名，確認使用相同的向量來命名，記得英文字母的大小寫在R中是有差別的！

*** =sample_code
```{r}
# 星期一至五的樸克牌贏錢金額
poker_vector <- c(140, -50, 20, -120, 240)

# 星期一至五的俄羅斯輪盤贏錢金額
roulette_vector <- c(-24, -50, 100, -350, 10)

# 用星期一至五命名poker_vector
names(poker_vector) <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")

# 用星期一至五命名roulette_vectors
```

*** =solution
```{r}
# 星期一至五的樸克牌贏錢金額
poker_vector <- c(140, -50, 20, -120, 240)

# 星期一至五的俄羅斯輪盤贏錢金額
roulette_vector <- c(-24, -50, 100, -350, 10)

# 用星期一至五命名poker_vector
names(poker_vector) <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")

# 用星期一至五命名roulette_vectors
names(roulette_vector) <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
```

*** =sct
```{r}
test_object("poker_vector",
            incorrect_msg = "\u4e0d\u9700\u8981\u66f4\u6539 `poker_vector`\u3002")
test_object("roulette_vector",
            incorrect_msg = "\u4e0d\u9700\u8981\u66f4\u6539 `roulette_vector`\u3002")
test_object("poker_vector",
            eq_condition = "equal",
            incorrect_msg = "\u4e0d\u9700\u8981\u66f4\u6539\u70ba `poker_vector` \u547d\u540d\u7684\u7a0b\u5f0f\uff0c\u628a\u6ce8\u610f\u529b\u96c6\u4e2d\u5728 `roulette_vector`\uff01")
test_object("roulette_vector",
            eq_condition = "equal",
            incorrect_msg = "\u78ba\u8a8d\u4f60\u6307\u6d3e\u6b63\u78ba\u7684\u547d\u540d\u7d66 `roulette_vector`\u3002\u7528\u547d\u540d `poker_vector` \u7684\u76f8\u540c\u5411\u91cf\u547d\u540d\u5373\u53ef\u3002")
success_msg("\u505a\u5f97\u597d\uff0c\u524d\u9032\u4e0b\u4e00\u500b\u7df4\u7fd2\uff01")
```


--- type:NormalExercise xp:100 skills:1 key:cfa4561b5f565645ab272a96838ae690d6ecf621
## 為向量命名 (2)

懶惰的人可以成為一個優秀的統計學家(假如你真的非常懶惰，你有很高的機率是那些天生統計學天才的一份子。)

在前一個練習你可能對於不停輸入星期幾感到無聊，其實有一個更有效率的方法，那就是把星期幾指派給一個**變數**！

如同你記錄樸克牌與俄羅斯輪盤贏錢金額，你也可以宣告一個變數包含星期幾的資訊，如此就可以重複使用它。

*** =instructions
- 包含星期幾的變數 `days_vector` 已經宣告好了。
- 使用 `days_vector` 為 `poker_vector` 與 `roulette_vector`命名。

*** =hint
如同使用 `names(poker_vector) <- days_vector` 來為 `poker_vector` 的元素命名一樣，對 `roulette_vector` 做一樣的事情。

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# 星期一至五的樸克牌贏錢金額
poker_vector <- c(140, -50, 20, -120, 240)

# 星期一至五的俄羅斯輪盤贏錢金額
roulette_vector <- c(-24, -50, 100, -350, 10)

# 變數days_vector
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
 
# 指派變數days_vector給roulette_vector與poker_vector
names(poker_vector) <-   
names(roulette_vector) <-
```

*** =solution
```{r}
# 星期一至五的樸克牌贏錢金額
poker_vector <- c(140, -50, 20, -120, 240)

# 星期一至五的俄羅斯輪盤贏錢金額
roulette_vector <- c(-24, -50, 100, -350, 10)

# 變數days_vector
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")

# 指派變數days_vector給roulette_vector與poker_vector
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector
```

*** =sct
```{r}
msg <- "\u4e0d\u9700\u8981\u66f4\u6539 `poker_vector` \u3001 `roulette_vector` \u6216 `days_vector`\u3002"
test_object("poker_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("roulette_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("days_vector", undefined_msg = msg, incorrect_msg = msg)

test_object("poker_vector",
            eq_condition = "equal",
            incorrect_msg = "\u78ba\u8a8d\u662f\u5426\u6307\u6d3e `days_vector` \u4f5c\u70ba `poker_vector` \u7684\u547d\u540d\u3002")
test_object("roulette_vector",
            eq_condition = "equal",
            incorrect_msg = "\u78ba\u8a8d\u662f\u5426\u6307\u6d3e `days_vector` \u4f5c\u70ba `roulette_vector`\u7684\u547d\u540d\u3002")
success_msg("\u505a\u5f97\u597d\uff01\u826f\u5fc3\u5efa\u8b70\uff1a\u6c38\u9060\u8a66\u8457\u907f\u514d\u5beb\u91cd\u8907\u7684\u7a0b\u5f0f\u3002\u524d\u9032\u4e0b\u4e00\u500b\u7df4\u7fd2\u4e26\u5b78\u7fd2\u5411\u91cf\u7684\u6578\u5b78\u904b\u7b97\uff01")
```


--- type:NormalExercise xp:100 skills:1 key:a0e5bb0a2dfc13b73a6edf7408aedaf100f156ef
## 計算加總贏錢金額

現在你有了命名過的樸克牌與俄羅斯輪盤的贏錢記錄，你可以開始做點資料分析魔法。

你心中有這幾個問題：
- 每日的總獲利或總損失為何？
- 這週總計有沒有賠錢？
- 在樸克牌與俄羅斯輪盤的各自表現如何？

要回答這些問題，你必須作一些向量的數學運算。

在R中相加2個向量會得到元素相加的結果，例如：

```
c(1, 2, 3) + c(4, 5, 6)
c(1 + 4, 2 + 5, 3 + 6)
c(5, 7, 9)
```

也可以用變數來代表向量：

```
a <- c(1, 2, 3) 
b <- c(4, 5, 6)
c <- a + b
```

*** =instructions
- 將 `A_vector` 與 `B_vector` 相加並指派給 `total_vector`。
- 將 `total_vector` 印出來檢視結果。

*** =hint
使用 `+` 相加 `A_vector` 與 `B_vector` ，並利用 `<-` 將結果指派給 `total_vector`。

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
A_vector <- c(1, 2, 3)
B_vector <- c(4, 5, 6)

# 將A_vector與B_vector相加
total_vector <- 
  
# 印出total_vector

```

*** =solution
```{r}
A_vector <- c(1, 2, 3)
B_vector <- c(4, 5, 6)

# 將A_vector與B_vector相加
total_vector <- A_vector + B_vector

# 印出total_vector
total_vector
```

*** =sct
```{r}
msg <- "\u4e0d\u9700\u8981\u66f4\u6539 `A_vector` \u6216 `B_vector` \u7684\u5167\u5bb9\uff01"
test_object("A_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("B_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("total_vector", incorrect_msg = "\u78ba\u8a8d `total_vector` \u662f\u5426\u70ba `A_vector` \u52a0 `B_vector`\u3002")
test_output_contains("total_vector", incorrect_msg = "\u5225\u5fd8\u4e86\u5370\u51fa `total_vector`\uff01 \u53ea\u8981\u52a0\u4e00\u884c `total_vector` \u5373\u53ef\u3002")
success_msg("\u505a\u5f97\u597d\uff0c\u524d\u9032\u4e0b\u4e00\u500b\u7df4\u7fd2\uff01")
```


--- type:NormalExercise xp:100 skills:1 key:647ae33cb77824ceb0b881a42da73a51dca46c95
## 計算加總贏錢金額 (2)

你現在瞭解R如何做向量的數學運算，該是把法拉利買回來的時候了！首先你需要了解這一週每日的總獲利或總損失，而每日的總獲利或總損失就是將每天在樸克牌與俄羅斯輪盤的贏錢金額加總。

其實就是把 `roulette_vector` 與 `poker_vector` 相加。

*** =instructions
將變數 `total_daily` 宣告為每日的總獲利或總損失(樸克牌與俄羅斯輪盤)。

*** =hint
跟前一個練習類似，將2個向量相加並指派給新變數 `total_daily`。

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# 星期一至五的樸克牌與俄羅斯輪盤贏錢金額
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# 宣告total_daily為每日的總獲利或總損失
total_daily <- 
```

*** =solution
```{r}
# 星期一至五的樸克牌與俄羅斯輪盤贏錢金額
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# 宣告total_daily為每日的總獲利或總損失
total_daily <- poker_vector + roulette_vector
```

*** =sct
```{r}
msg = "\u4e0d\u9700\u8981\u66f4\u6539 `poker_vector` \u8207 `roulette_vector` \u7684\u5ba3\u544a\u8207\u547d\u540d\u3002"
test_object("days_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("roulette_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)

test_object("total_daily", incorrect_msg = "\u78ba\u8a8d\u4f60\u5c07 `poker_vector` \u8207 `roulette_vector` \u76f8\u52a0\u5f8c\u6307\u6d3e\u7d66 `total_daily`\u3002")

success_msg("\u592a\u68d2\u4e86\uff0c\u524d\u9032\u4e0b\u4e00\u500b\u7df4\u7fd2\uff01")
```


--- type:NormalExercise xp:100 skills:1 key:ab4e6dfbddc58056dbc98092c89bf568302eecae
## 計算加總贏錢金額 (3)

根據前一個練習，看起來是個輸贏參半的一週，你懷疑是否有可能其實整體結算下來上週是輸錢的呢？

能夠回答這個問題的函數是[`sum()`](http://www.rdocumentation.org/packages/base/functions/sum)。它可以加總向量中所有的元素，例如計算在樸克牌的總獲利或總損失：

```
total_poker <- sum(poker_vector)
```

*** =instructions
- 計算在俄羅斯輪盤的總獲利或總損失並將結果指派給 `total_roulette`。
- 有了樸克牌與俄羅斯輪盤的總獲利或總損失後，就可以簡單計算 `total_week` (即這一週的總獲利或總損失)。
- 印出`total_week`。

*** =hint
使用[`sum()`](http://www.rdocumentation.org/packages/base/functions/sum)函數得到　`roulette_vector`　的總合， `total_week` 就是 `roulette_vector` 加 `poker_vector`。

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# 星期一至五的樸克牌與俄羅斯輪盤贏錢金額
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# 樸克牌的總贏錢金額
total_poker <- sum(poker_vector)

# 俄羅斯輪盤的總贏錢金額
total_roulette <-  

# 總贏錢金額
total_week <- 

# 印出total_week
  
```

*** =solution
```{r}
# 星期一至五的樸克牌與俄羅斯輪盤贏錢金額
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# 樸克牌的總贏錢金額
total_poker <- sum(poker_vector)

# 俄羅斯輪盤的總贏錢金額
total_roulette <-  sum(roulette_vector)

# 總贏錢金額
total_week <- total_roulette + total_poker

# 印出total_week
total_week
```

*** =sct
```{r}
msg = "不需要更改 `poker_vector` and `roulette_vector`　的宣告與命名。"
test_object("days_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("roulette_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("total_poker", 
            incorrect_msg = "確認是否有將　`poker_vector`　的總和指派給 `total_poker`。")
test_object("total_roulette",
            incorrect_msg = "確認是否有將 `total_roulette` 的總和指派給 `roulette_vector`。")
test_object("total_week",
            incorrect_msg = "確認是否有將 `total_roulette` 加 `total_poker` 的結果指派給 `total_week`。")

test_output_contains("total_week", incorrect_msg = "別忘了再寫一行 `total_week` 把結果印出來。")
success_msg("做得好，但這個結果真是...")
```


--- type:NormalExercise xp:100 skills:1 key:d4aec72e46e130bfc7e3992f07bd6d6cc3b8179b
## Comparing total winnings

Oops, it seems like you are losing money. Time to rethink and adapt your strategy! This will require some deeper analysis... 

After a short brainstorm in your hotel's jacuzzi, you realize that a possible explanation might be that your skills in roulette are not as well developed as your skills in poker. So maybe your total gains in poker are higher (or `>` ) than in roulette.

*** =instructions
- Calculate `total_poker` and `total_roulette` as in the previous exercise. Use the `sum()` function twice.
- Check if your total gains in poker are higher than for roulette by using a comparison. Simply print out the result of this comparison. What do you conclude, should you focus on roulette or on poker?

*** =hint
- You partly calculated the answer to this question in the previous exercise already!
- To check if 6 is larger than 5, you type `6 > 5`. This returns a logical value (`TRUE` or `FALSE`).

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Calculate total gains for poker and roulette
total_poker <-
total_roulette <-

# Check if you realized higher total gains in poker than in roulette 

```

*** =solution
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Calculate total gains for poker and roulette
total_poker <- sum(poker_vector)
total_roulette <- sum(roulette_vector)

# Check if you realized higher total gains in poker than in roulette
total_poker > total_roulette
```

*** =sct
```{r}
msg <- "Do not change anything about the definition and naming of `poker_vector` and `roulette_vector`."
test_object("days_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("roulette_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)

test_object("total_poker", 
            incorrect_msg = "Make sure that you assign to `total_poker` the sum of the `poker_vector`. Use `sum()`.")
test_object("total_roulette",
            incorrect_msg = "Make sure that you assign to `total_roulette` the sum of the `roulette_vector`. Use `sum()`.")
test_output_contains("total_poker > total_roulette",
                     incorrect_msg = "Have you correctly carried out the comparison? To check if `total_poker` is greater than `total_roulette`, you can use `total_poker > total_roulette`.")
success_msg("Good job! Continue to the next exercise.")
```


--- type:NormalExercise xp:100 skills:1 key:cf3480826ff4ed5aa06b4fccf8fa19b30e2f02f6
## Vector selection: the good times

Your hunch seemed to be right. It appears that the poker game is more your cup of tea than roulette. 

Another possible route for investigation is your performance at the beginning of the working week compared to the end of it. You did have a couple of Margarita cocktails at the end of the week... 

To answer that question, you only want to focus on a selection of the `total_vector`. In other words, our goal is to select specific elements of the vector. To select elements of a vector (and later matrices, data frames, ...), you can use square brackets. Between the square brackets, you indicate what elements to select. For example, to select the first element of the vector, you type `poker_vector[1]`. To select the second element of the vector, you type `poker_vector[2]`, etc. Notice that the first element in a vector has index 1, not 0 as in many other programming languages.

*** =instructions
Assign the poker results of Wednesday to the variable `poker_wednesday`.

*** =hint
Wednesday is the third element of `poker_vector`, and can thus be selected with `poker_vector[3]`.

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Define a new variable based on a selection
poker_wednesday <- 
```

*** =solution
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Define a new variable based on a selection
poker_wednesday <- poker_vector[3]
```

*** =sct
```{r}
msg = "Do not change anything about the definition and naming of `poker_vector` and `roulette_vector`."
test_object("days_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("roulette_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_wednesday", 
            undefined_msg = "Please make sure to define a variable `poker_wednesday`.",
            incorrect_msg = "It looks like `poker_wednesday` does not contain the correct value of the `poker_vector`.")
success_msg("Great! R also makes it possible to select multiple elements from a vector at once. Learn how in the next exercise!")
```


--- type:NormalExercise xp:100 skills:1 key:961b3b1c8a4721c71a6f099daacf17156b59b6a1
## Vector selection: the good times (2)

How about analyzing your midweek results? 

To select multiple elements from a vector, you can add square brackets at the end of it. You can indicate between the brackets what elements should be selected. For example: suppose you want to select the first and the fifth day of the week: use the vector `c(1, 5)` between the square brackets. For example, the code below selects the first and fifth element of `poker_vector`:

```
poker_vector[c(1, 5)]
```

*** =instructions
Assign the poker results of Tuesday, Wednesday and Thursday to the variable `poker_midweek`.

*** =hint
Use the vector `c(2, 3, 4)` between square brackets to select the correct elements of `poker_vector`.

*** =pre_exercise_code
```{r}
# no pec
``` 

*** =sample_code
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Define a new variable based on a selection
poker_midweek <- 
```

*** =solution
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Define a new variable based on a selection
poker_midweek <- poker_vector[c(2, 3, 4)]
```

*** =sct
```{r}
msg = "Do not change anything about the definition and naming of `poker_vector` and `roulette_vector`."
test_object("days_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("roulette_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_midweek", 
            incorrect_msg = "It looks like `poker_midweek` does not contain the correct values from `poker_vector`. You can use the vector `c(2, 3, 4)` inside square brackets.")
success_msg("Well done! Continue to the next exercise to specialize in vector selection some more!");
```


--- type:NormalExercise xp:100 skills:1 key:30b0e8c9fe371d8f3f1391c1088fce05c195c52a
## Vector selection: the good times (3)

Selecting multiple elements of `poker_vector` with `c(2, 3, 4)` is not very convenient. Many statisticians are lazy people by nature, so they created an easier way to do this: `c(2, 3, 4)` can be abbreviated to`2:4`, which generates a vector with all natural numbers from 2 up to 4.

So, another way to find the mid-week results is `poker_vector[2:4]`. Notice how the vector `2:4` is placed between the square brackets to select element 2 up to 4.

*** =instructions
Assign to `roulette_selection_vector` the roulette results from Tuesday up to Friday; make use of `:` if it makes things easier for you.

*** =hint
Assign a selection of `roulette_vector` to `roulette_selection_vector` by placing `2:5` between square brackets.

*** =sample_code
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Define a new variable based on a selection
roulette_selection_vector <- 
```

*** =solution
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Define a new variable based on a selection
roulette_selection_vector <- roulette_vector[2:5]
```

*** =sct

```{r}
msg = "Do not change anything about the definition and naming of `poker_vector` and `roulette_vector`."
test_object("days_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("roulette_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("roulette_selection_vector", 
            undefined_msg = "Please make sure to define a variable `roulette_selection_vector`.",
            incorrect_msg = "It looks like `roulette_selection_vector` does not contain the correct selection from `roulette_vector`. Make sure to to use the right indexes.")
success_msg("Awesome! The colon operator is extremely useful and very often used in R programming, so remember it well. Proceed to the next exercise.")
```


--- type:NormalExercise xp:100 skills:1 key:479dfd0f8bc1f275c5cfd65b9f801be9f6498855
## Vector selection: the good times (4)

Another way to tackle the previous exercise is by using the names of the vector elements (Monday, Tuesday, ...) instead of their numeric positions. For example, 

```
poker_vector["Monday"]
```

will select the first element of `poker_vector` since `"Monday"` is the name of that first element.

Just like you did in the previous exercise with numerics, you can also use the element names to select multiple elements, for example: 

```
poker_vector[c("Monday","Tuesday")]
```

*** =instructions
- Select the first three elements in `poker_vector` by using their names: `"Monday"`, `"Tuesday"` and `"Wednesday"`. Assign the result of the selection to `poker_start`.
- Calculate the average of the values in `poker_start` with the [`mean()`](http://www.rdocumentation.org/packages/base/functions/mean) function. Simply print out the result so you can inspect it.

*** =hint
- You can use `c("Monday", "Tuesday", "Wednesday")` inside square brackets to subset `poker_vector` appropriately.
- You can use `mean(poker_start)` to get the mean of the elements in `poker_start`. You do not need the mean of all poker elements, but only of the first three days.

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Select poker results for Monday, Tuesday and Wednesday
poker_start <- 
  
# Calculate the average of the elements in poker_start

```

*** =solution
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Select poker results for Monday, Tuesday and Wednesday
poker_start <- poker_vector[c("Monday", "Tuesday", "Wednesday")]
  
# Calculate the average of the elements in poker_start
mean(poker_start)
```

*** =sct
```{r}
msg = "Do not change anything about the definition and naming of `poker_vector` and `roulette_vector`."
test_object("days_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("roulette_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_start", 
            incorrect_msg = "It looks like `poker_start` does not contain the first three values of `poker_vector`. You can use `c(\"Monday\", \"Tuesday\", \"Wednesday\")` inside square brackets to do this.")
test_output_contains("mean(poker_start)", incorrect_msg = "Have you correctly calculated the average of the values in `poker_start` and printed it out? Use `mean(poker_start)`.")
success_msg("Good job! Apart from subsetting vectors by index or by name, you can also subset vectors by comparison. The next exercises will show you how!");
```


--- type:NormalExercise xp:100 skills:1 key:11850f807f9b0fad101a88004291b7ced6397083
## Selection by comparison - Step 1

By making use of comparison operators, we can approach the previous question in a more proactive way. 

The (logical) comparison operators known to R are:

- `<` for less than
- `>` for greater than
- `<=` for less than or equal to
- `>=` for greater than or equal to
- `==` for equal to each other
- `!=` not equal to each other

As seen in the previous chapter, stating `6 > 5` returns `TRUE`. The nice thing about R is that you can use these comparison operators also on vectors. For example:

```
> c(4, 5, 6) > 5
[1] FALSE FALSE TRUE
```

This command tests for every element of the vector if the condition stated by the comparison operator is `TRUE` or `FALSE`.

*** =instructions
- Check which elements in `poker_vector` are positive (i.e. > 0) and assign this to `selection_vector`. 
- Print out `selection_vector` so you can inspect it. The printout tells you whether you won (`TRUE`) or lost (`FALSE`) any money for each day.

*** =hint
In order to check for which days your poker gains are positive, R should check for each element of `poker_vector` whether it is larger than zero. `some_vector > 0` is the way to tell R what you are after.

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Which days did you make money on poker?
selection_vector <- 
  
# Print out selection_vector

```

*** =solution
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Which days did you make money on poker?
selection_vector <- poker_vector > 0
  
# Print out selection_vector
selection_vector
```

*** =sct
```{r}
msg <- "Do not change anything about the definition and naming of `poker_vector` and `roulette_vector`."
test_object("days_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("roulette_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)

test_object("selection_vector", incorrect_msg = "It looks like `selection_vector` does not contain the correct result. Remember that R uses element wise operations for vectors.")
test_output_contains("selection_vector", incorrect_msg = "Don't forget to print out `selection_vector` by writing the variable name on a new line.")
success_msg("Great!")
```


--- type:NormalExercise xp:100 skills:1 key:8521f1e1993a6154e68ccfa75e29e517955343ac
## Selection by comparison - Step 2

Working with comparisons will make your data analytical life easier. Instead of selecting a subset of days to investigate yourself (like before), you can simply ask R to return only those days where you realized a positive return for poker. 

In the previous exercises you used `selection_vector <- poker_vector > 0` to find the days on which you had a positive poker return. Now, you would like to know not only the days on which you won, but also how much you won on those days. 

You can select the desired elements, by putting `selection_vector` between the square brackets that follow `poker_vector`:

```
poker_vector[selection_vector]
```

R knows what to do when you pass a logical vector in square brackets: it will only select the elements that correspond to `TRUE` in `selection_vector`.

*** =instructions
Use `selection_vector` in square brackets to assign the amounts that you won on the profitable days to the variable `poker_winning_days`.

*** =hint
Use `poker_vector[selection_vector]` to select the desired elements from `poker_vector`, and assign the result to `poker_winning_days`.

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Which days did you make money on poker?
selection_vector <- poker_vector > 0

# Select from poker_vector these days
poker_winning_days <- 
```

*** =solution
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Which days did you make money on poker?
selection_vector <- poker_vector > 0

# Select from poker_vector these days
poker_winning_days <- poker_vector[selection_vector]
```

*** =sct
```{r}
msg = "Do not change anything about the definition and naming of `poker_vector` and `roulette_vector`."
test_object("days_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("roulette_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("selection_vector", incorrect_msg = "Don't change the way `selection_vector` is calculated.")
test_object("poker_winning_days",
            incorrect_msg =  "It looks like `poker_winning_days` does not contain the correct result. Use `poker_vector[selection_vector]`.")
success_msg("Good job! Continue to the next exercise.")
```


--- type:NormalExercise xp:100 skills:1 key:921c6ad3b79b9b3532c7f4201d5202516b755324
## Advanced selection

Just like you did for poker, you also want to know those days where you realized a positive return for roulette.

*** =instructions
- Create the variable `selection_vector`, this time to see if you made profit with roulette for different days.
- Assign the amounts that you made on the days that you ended positively for roulette to the variable `roulette_winning_days`. This vector thus contains the positive winnings of `roulette_vector`.

*** =hint
Once you've correctly calculated `selection_vector`, you can again use `roulette_vector[selection_vector]` to select the positive results from `roulette_vector`.

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Which days did you make money on roulette?
selection_vector <-

# Select from roulette_vector these days
roulette_winning_days <- 
```

*** =solution
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Which days did you make money on roulette?
selection_vector <- roulette_vector > 0

# Select from roulette_vector these days
roulette_winning_days <- roulette_vector[selection_vector]
```

*** =sct
```{r}
msg = "Do not change anything about the definition and naming of `poker_vector` and `roulette_vector`."
test_object("days_vector", undefined_msg = msg, incorrect_msg = msg)
test_object("poker_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("roulette_vector", eq_condition = "equal", undefined_msg = msg, incorrect_msg = msg)
test_object("selection_vector", 
            incorrect_msg = "It looks like `selection_vector` does not contain the correct result. Use `roulette_vector > 0`.")
test_object("roulette_winning_days",
            incorrect_msg = "It looks like `roulette_winning_days` does not contain the correct result. Use `roulette_vector[selection_vector]`.")

success_msg("Great! This exercise concludes the chapter on vectors. The next chapter will introduce you to the two-dimensional version of vectors: matrices.")
```



