--- 
title_meta  : 第一章
title       : 基本介紹
description : "你會初次接觸R，學習到如何使用R做計算以及如何宣告變數，也會學習R的基本資料類型，讓我們趕快開始吧！"

--- type:NormalExercise xp:100 skills:1
## 熟悉環境

你要在右邊的編輯區輸入R程式碼來完成練習，當你按下Submit Answer按鈕後，每一行程式碼都會被編譯且執行，然後你將會得到正確或錯誤的訊息，R程式碼的輸出結果會呈現在右下角的R Console視窗中。

R使用 `#` 來加入註解，讓你與其他人可以更快了解這段R程式碼的用途，就跟Twitter一樣！註解不會被執行故不影響結果，例如在右方編輯區的_計算 3 + 4_就是一個註解。

你也可以直接在R Console視窗中執行R程式碼，這是一個測試語法是否正確的好方法。

*** =instructions
- 在右邊的編輯區已經有了一些範例，你看得出來哪些是會被執行的R程式碼，哪些是不會被執行的註解嗎？
- 加入一行R程式碼計算6加12，然後按下Submit Answer按鈕。

*** =hint
加入一行R程式碼計算6加12，就像範例一樣！

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# 計算 3 + 4
3 + 4

# 計算 6 + 12

```

*** =solution
```{r}
# 計算 3 + 4
3 + 4

# 計算 6 + 12
6 + 12
```

*** =sct
```{r}
test_output_contains("7", incorrect_msg = "\u4e0d\u9700\u8981\u79fb\u9664\u8a08\u7b973\u52a04\u7684\u7a0b\u5f0f\u78bc\uff0c\u52a0\u53e6\u5916\u4e00\u884c\u7a0b\u5f0f\u78bc\u8a08\u7b976\u52a012\u5373\u53ef\u3002")
test_output_contains("18", incorrect_msg = "\u78ba\u5b9a\u4f60\u6709\u52a0\u4e86\u4e00\u884c\u7a0b\u5f0f\u78bc\u8a08\u7b976\u52a012\uff0c\u6ce8\u610f\u4e0d\u8981\u5728\u7a0b\u5f0f\u78bc\u524d\u9762\u52a0\u4e0a `#`\uff0c\u5426\u5247\u5c07\u4e0d\u6703\u88ab\u57f7\u884c\uff01")
success_msg("\u592a\u68d2\u4e86\uff01\u770b\u5230console\u5982\u4f55\u5448\u73fe\u4f60\u9001\u51fa\u7684\u7a0b\u5f0f\u4e86\u55ce\uff1f\u73fe\u5728\u4f60\u5df2\u7d93\u719f\u6089\u4e86\u4ecb\u9762\uff0c\u63a5\u4e0b\u4f86\u6211\u5011\u4f86\u6df1\u5165\u7814\u7a76R\u5427\uff01")
```

--- type:NormalExercise xp:100 skills:1
## Arithmetic with R

In its most basic form, R can be used as a simple calculator. Consider the following arithmetic operators:

- Addition: `+`
- Subtraction: `-`
- Multiplication: `*`
- Division: `/`
- Exponentiation: `^`
- Modulo: `%%`

The last two might need some explaining:
- The `^` operator raises the number to its left to the power of the number to its right: for example `3^2` is 9.
- The modulo returns the remainder of the division of the number to the left by the number on its right, for example 5 modulo 3 or `5 %% 3` is 2.

With this knowledge, follow the instructions below to complete the exercise.

*** =instructions
- Type `2^5` in the editor to calculate 2 to the power 5.
- Type `28 %% 6` to calculate 28 modulo 6.
- Click 'Submit Answer' and have a look at the R output in the console.
- Note how the `#` symbol is used to add comments on the R code.

*** =hint
Another example of the modulo operator: `9 %% 2` equals `1`.

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# An addition
5 + 5 

# A subtraction
5 - 5 

# A multiplication
3 * 5

 # A division
(5 + 5) / 2 

# Exponentiation


# Modulo

```

*** =solution
```{r}
# An addition
5 + 5

# A subtraction
5 - 5 

# A multiplication
3 * 5

 # A division
(5 + 5) / 2 

# Exponentiation
2 ^ 5

# Modulo
28 %% 6
```

*** =sct
```{r}
msg = "Do not remove the other arithmetic examples!"
test_output_contains("5 + 5", incorrect_msg = msg)
test_output_contains("5 - 5", incorrect_msg = msg)
test_output_contains("(5 + 5)/2", incorrect_msg = msg)
test_output_contains("2^5", incorrect_msg = "The exponentiation example is not correct. Make sure to read the instructions carefully.")
test_output_contains("28 %% 6", incorrect_msg = "There seems to be an issue with the modulo example. Make sure to read the instructions carefully.")
success_msg("Great! Head over to the next exercise.")
```


--- type:NormalExercise xp:100 skills:1
## Variable assignment 

A basic concept in (statistical) programming is called a **variable**. 

A variable allows you to store a value (e.g. 4) or an object (e.g. a function description) in R. You can then later use this variable's name to easily access the value or the object that is stored within this variable. 

You can assign a value 4 to a variable `my_var` with the command

```
my_var <- 4
```

*** =instructions
Over to you: complete the code in the editor such that it assigns the value 42 to the variable `x` in the editor. Click 'Submit Answer'. Notice that when you ask R to print `x`, the value 42 appears.

*** =hint
Look at how the value 4 was assigned to `my_variable` in the exercise's assignment. Do the exact same thing in the editor, but now assign 42 to the variable `x`.

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Assign the value 42 to x
x <- 

# Print out the value of the variable x
x
```

*** =solution
```{r}
# Assign the value 42 to x
x <- 42

# Print out the value of the variable x
x
```

*** =sct
```{r}
test_object("x", undefined_msg = "Make sure to define a variable `x`.",
            incorrect_msg = "Make sure that you assign the correct value to `x`.") 
success_msg("Good job! Have you noticed that R does not print the value of a variable to the console when you did the assignment? `x <- 42` did not generate any output, because R assumes that you will be needing this variable in the future. Otherwise you wouldn't have stored the value in a variable in the first place, right? Proceed to the next exercise!")
```


--- type:NormalExercise xp:100 skills:1
## Variable assignment (2)

Suppose you have a fruit basket with five apples. As a data analyst in training, you want to store the number of apples in a variable with the name `my_apples`. 

*** =instructions
- Type the following code in the editor: `my_apples <- 5`. This will assign the value 5 to `my_apples`.
- Type: `my_apples` below the second comment. This will print out the value of `my_apples`.
- Click 'Submit Answer', and look at the console: you see that the number 5 is printed. So R now links the variable `my_apples` to the value 5.

*** =hint
Remember that if you want to assign a number or an object to a variable in R, you can make use of the assignment operator `<-`. Alternatively, you can use `=`, but `<-` is widely preferred in the R community.

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Assign the value 5 to the variable my_apples


# Print out the value of the variable my_apples

```

*** =solution
```{r}
# Assign the value 5 to the variable my_apples
my_apples <- 5

# Print out the value of the variable my_apples
my_apples
```

*** =sct
```{r}
test_object("my_apples", 
            undefined_msg = "Please make sure to define a variable `my_apples`.",
            incorrect_msg = "Make sure that you assign the correct value to `my_apples`.")
test_output_contains("my_apples", 
                     incorrect_msg = "Have you explicitly told R to print out the `my_apples` variable to the console?")
success_msg("Great! Continue to the next exercise!")
```


--- type:NormalExercise xp:100 skills:1
## Variable assignment (3)

Every tasty fruit basket needs oranges, so you decide to add six oranges. As a data analyst, your reflex is to immediately create the variable `my_oranges` and assign the value 6 to it. Next, you want to calculate how many pieces of fruit you have in total. Since you have given meaningful names to these values, you can now code this in a clear way: 
```
my_apples + my_oranges
```

*** =instructions
- Assign to `my_oranges` the value 6.
- Add the variables `my_apples` and `my_oranges` and have R simply print the result.
- Combine the variables `my_apples` and `my_oranges` into a new variable `my_fruit`, which is the total amount of fruits in your fruit basket.

*** =hint
`my_fruit` is just the sum of `my_apples` and `my_oranges`. You can use the `+` operator to sum the two and `<-` to assign that value to the variable `my_fruit`.

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Assign a value to the variables called my_apples and my_oranges
my_apples <- 5


# Add these two variables together and print the result


# Create the variable my_fruit

```

*** =solution
```{r}
# Assign a value to the variables called my_apples and my_oranges
my_apples  <- 5
my_oranges <- 6

# Add these two variables together and print the result
my_apples + my_oranges

# Create the variable my_fruit
my_fruit <- my_apples + my_oranges
```

*** =sct
```{r}
test_object("my_apples", 
            undefined_msg = "Please make sure to define a variable `my_apples`.",
            incorrect_msg = "Do not change the assignment of the `my_apples` variable!")
test_object("my_oranges", 
            undefined_msg = "Have you defined a variable `my_oranges`?",
            incorrect_msg = "Have you assigned the correct value to the variable `my_oranges`?")
test_output_contains("my_apples + my_oranges",
                     incorrect_msg = "Make sure to write `my_apples + my_oranges` on a new line; this will print out the result of the sum.")
test_object("my_fruit",
            undefined_msg = "Please make sure to define a variable `my_fruit`.",
            incorrect_msg = "Make sure that you assign the correct value to `my_fruit`.")
success_msg("Nice one! The great advantage of doing calculations with variables is reusability. If you just change `my_apples` to equal 12 instead of 5 and rerun the script, `my_fruit` will automatically update as well. Continue to the next exercise.")
```


--- type:NormalExercise xp:100 skills:1
## Apples and oranges

Common knowledge tells you not to add apples and oranges. But hey, that is what you just did, no :-)? The `my_apples` and `my_oranges` variables both contained a number in the previous exercise. The `+` operator works with numeric variables in R. If you really tried to add "apples" and "oranges", and assigned a text value to the variable `my_oranges` (see the editor), you would be trying to assign the addition of a numeric and a character variable to the variable `my_fruit`. This is not possible.

*** =instructions
- Click 'Submit Answer' and read the error message. Make sure to understand why this did not work.
- Adjust the code so that R knows you have 6 oranges and thus a fruit basket with 11 pieces of fruit.

*** =hint
You have to assign the numeric value `6` to the `my_oranges` variable instead of the character value `"six"`. Note how the quotation marks are used to indicate that `"six"` is a character.

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Assign a value to the variable called my_apples
my_apples <- 5 

# Print out the value of my_apples
my_apples       

# Assign a value to the variable my_oranges and print it out
my_oranges <- "six" 
my_oranges 

# New variable that contains the total amount of fruit
my_fruit <- my_apples + my_oranges 
my_fruit
```

*** =solution
```{r}
# Assign a value to the variable called my_apples
my_apples <- 5  

# Print out the value of answer
my_apples  

# Assign a value to the variable my_oranges and print it out
my_oranges <- 6
my_oranges 

# New variable that contains the total amount of fruit
my_fruit <- my_apples + my_oranges 
my_fruit
```

*** =sct
```{r}
test_error()
test_object("my_oranges",
            incorrect_msg = "Make sure that you assign the correct value to `my_oranges`. Strings and numbers are different things!")
test_output_contains("my_apples + my_oranges", 
                     incorrect_msg = "The output does not contain the result of adding `my_apples` and `my_oranges`.")
test_object("my_fruit",
            incorrect_msg = "Make sure that you assign the correct value to `my_fruit`.")
success_msg("Awesome, keep up the good work! Continue to the next exercise.")
```


--- type:NormalExercise xp:100 skills:1
## Basic data types in R

R works with numerous data types. Some of the most basic types to get started are:

- Decimals values like `4.5` are called **numerics**.
- Natural numbers like `4` are called **integers**. Integers are also numerics.
- Boolean values (`TRUE` or `FALSE`) are called **logical**.
- Text (or string) values are called **characters**.

Note how the quotation marks on the right indicate that "some text" is a character.

*** =instructions
Change the value of the:
- `my_numeric` variable to `42`.
- `my_character` variable to `"universe"`. Note that the quotation marks indicate that `"universe"` is a character.
- `my_logical` variable to `FALSE`.

Note that R is case sensitive!

*** =hint 
Replace the values in the editor with the values that are provided in the exercise. For example: 
`my_numeric <- 42` assigns the value 42 to the variable `my_numeric`. 

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Change my_numeric to be 42
my_numeric <- 42.5

# Change my_character to be "universe"
my_character <- "some text"

# Change my_logical to be FALSE
my_logical <- TRUE
```

*** =solution
```{r}
# Change my_numeric to be 42
my_numeric <- 42

# Change my_character to be "universe"
my_character <- "universe"

# Change my_logical to be FALSE
my_logical <- FALSE
```

*** =sct
```{r}
test_object("my_numeric", incorrect_msg = "Have you correctly changed the declaration of `my_numeric` so it contains the value 42?")
test_object("my_character", incorrect_msg = "Have you correctly changed `my_character` to `\"universe\"`. Don't forget the quotes!")
test_object("my_logical", incorrect_msg = "Have you correctly changes `my_logical` to `FALSE`? All letters of `FALSE` should be capitalized!")
success_msg("Great work! Continue to the next exercise.")
```


--- type:NormalExercise xp:100 skills:1
## What's that data type?

Do you remember that when you added `5 + "six"`, you got an error due to a mismatch in data types? You can avoid such embarrassing situations by checking the data type of a variable beforehand. You can do this with the `class()` function, as the code on the right shows.

*** =instructions
Complete the code in the editor and also print out the classes of `my_character` and `my_logical`. 

*** =hint
The code that prints the data type of `my_numeric` is already included; do a similar things for `my_character` and `my_logical`. 

*** =pre_exercise_code
```{r}
# no pec
```

*** =sample_code
```{r}
# Declare variables of different types
my_numeric <- 42
my_character <- "universe"
my_logical <- FALSE 

# Check class of my_numeric
class(my_numeric)

# Check class of my_character


# Check class of my_logical

```

*** =solution
```{r}
# Declare variables of different types:
my_numeric <- 42
my_character <- "universe"
my_logical <- FALSE

# Check class of my_numeric
class(my_numeric)

# Check class of my_character
class(my_character)

# Check class of my_logical
class(my_logical)
```

*** =sct
```{r}
msg <- "Do not change the declaration of the variables!"
lapply(c("my_numeric", "my_character", "my_logical"), test_object, undefined_msg = msg, incorrect_msg = msg)
patt <- "Have you included `class(%1$s)` to print out the data type of `%1$s`?"
test_output_contains("class(my_numeric)",
                     incorrect_msg = "Do not remove the code that prints out the type of `my_numeric`.")
test_output_contains("class(my_character)",
                     incorrect_msg = sprintf(patt, "my_character"))
test_output_contains("class(my_logical)",
                     incorrect_msg = sprintf(patt, "my_logical"))
success_msg("Congratulations! This was the last exercise for this chapter. Head over to the next chapter to get immersed in the world of vectors!")
```



